Equilibria and Convergence of Fictitious Play on Network Aggregative Games

### 2021-05-24 Documents/FP in NAGs/neurips_2021.tex
Up to Date Refs
various edits

  In this section we present our main results. First, we establish the existence of a Nash Equilibrium in the NA game, as in Def. \refname{def::NE}. Then we show that the Fictitious Play dynamic on the NA game admits solutions (i.e. the NA-CTFP exists). Finally, we show that NA-CTFP reaches a fixed point when the NA game is zero-sum and that, when the network has no self-loops (i.e. is simple), NA-CTFP reaches a Nash Equilibrium. For the sake of brevity, we defer the proofs of our statements, as well as the standard topological arguments used to derive them to the Supplementary Material (Sections (S4 - S6)).

  As a reminder, the NE condition (Def. \ref{def::NE}) states
%
  \begin{align}
    \NE{\mu} &\in \arg\max_{x \in \Delta_\mu} u^\mu(x, w^{\mu \mu}x + \sum_{\nu \in N^\mu} w^{\mu \nu} \NE{\nu}) \nonumber \\
    & =: \arg\max_{x \in \Delta_i} \bar{u}^\mu(x, \sum_{\nu \in N^\mu} w^{\mu \nu} \NE{\nu})
  \end{align}

  where we can find $\bar{u}_i$ through the following argument

  \begin{align}
    u^\mu(x, w^{\mu \mu} x + \sum_{\nu \in N^\nu} w_{\mu \nu} \NE{\nu}) & = x \cdot A^\mu (w^{\mu \mu} x + \sum_{\nu \in N^\mu} w_{\mu \nu} \NE{\nu}) \\
     & = x \cdot (w^{\mu \mu} A^\mu)  x + \sum_{\nu \in N^\mu} u^{\mu \nu}(x, \NE{\nu}) \\
     & =: \bar{u}^\mu(x, \sum_{\nu \in N^\mu} w^{\mu \nu} \NE{\nu}), \nonumber
  \end{align}

  where $u^{\mu \nu}(\xmu, x^\nu) = \xmu \cdot A^\mu x^\nu$. Note
  that, in order to get this formulation, we had to use the assumption
  of payoffs being bilinear so that we could separate out the term in
  the weighted sum involving $x$ from $\bar{x}^\nu$.

@@

  \begin{theorem}[Existence of NE]
    Under the assumption (II), namely that the payoff function achieves a bilinear property, a
    Nash Equilibrium $\{\bar{x}^\mu\}_{\mu \in \agentset}$ exists.
  \end{theorem}

@@

With the existence of the NA-CTFP in place, we can show that it converges
to a fixed point. In particular, let $\Omega(\alpha)$ be the set of
all limit points for $\alpha(t)$. Then, a NA-CTFP path is said to have
converged if $\Omega(\alpha)$ is contained within the set of Nash
Equilibria of the game. If this is for any such NA-CTFP path, then the
game is said to have the \emph{CTFP property}. We adapt the techniques
of (Ewerhart 2020) to prove that zero-sum NA games have the CTFP
property.

  \begin{theorem}
    Any zero-sum NA game has the property that, for any NA-CTFP path $m$, the corresponding $\alpha(t; m)$ converges to a set of fixed points.
  \end{theorem}

  We now point out that, if we choose $w^{\mu \mu}$ to be zero for all $\mu$, then the final inequality yields that, for all $\mu$

  \begin{equation}
    u^\mu(y, \sum_{\nu \in N^\mu} \wmunu \xnu_\infty) \leq u^\mu(\xmu_\infty, \sum_{\nu \in N^\mu} \wmunu \xnu_\infty)
  \end{equation}

  which is precisely the Nash Equilibrium condition in the NA game. This leads to the next result

  \begin{corollary}
    With the additional assumption that, for all agents $\mu$, all zero-sum NA games have the CTFP property
  \end{corollary}

@@

  In this section we aim to find some convergence structure for the
  case in which the NA game is not necessarily zero-sum. In
  particular, we show that the NA-CTFP process converges to the set of
  coarse correlated equilibria \cite{Nisan2007}.
  %
  \begin{definition}
    A distribution $\mathcal{D}$ over the joint action set $S =
    \times_\mu S^\mu$ is called a \emph{coarse correlated equilibrium}
    (CCE) if, for all $\mu$
    \begin{equation}
      \mathbb{E}_{s \sim \mathcal{D}}[u^\mu (s^\mu, s^{- \mu})] \geq
      \mathbb{E}_{x \sim \mathcal{D}}[u^\mu (j, s^{-
          \mu})] \hspace{1cm} \forall j \in S^\mu.
    \end{equation}
  \end{definition}

@@

  For an NA game, if a set of actions $s = (s^1, \ldots, s^N)$ \fb{$s$ is normally used for actions} is
  drawn from a joint probability distribution $\mathcal{D}$, then
  there is a corresponding set of reference vectors $\sigma =
  (\sigma^1, \ldots, \sigma^N)$, where $\sigma^\mu = \sum_{\nu \in
    N^\mu} \wmunu s^\nu$.  Therefore, $\mathcal{D}$ is a probability
  distribution over all actions and all references.  Consider, then, a
  vector of joint distributions over actions and references which is
  generated by NA-CTFP. In particular, if by playing with NA-CTFP, the
  agents reach the state $(\xmu)_{i = 1}^N$ with references
  $(\refmu)_{i = 1}^N$, this is the vector $\mathcal{D} =
  (\mathcal{D}^1, ..., \mathcal{D}^N)$ such that
  $(\mathcal{D}^\mu)_{ij} = \xmu_i \refmu_j$. Then, the expected
  payoff that the agent would receive for playing this strategy is

  \begin{align}
    u^\mu(\xmu, \refmu) & = \xmu \cdot A^\mu \refmu \nonumber \\
    & = \sum_{i, j} (A^\mu)_{ij} \xmu_i \refmu_j \nonumber 
  \end{align}

  As such, we would say that NA-CTFP has converged to the set of CCE if, in the limit of $t
  \rightarrow \infty$, we have that for all $\mu$

  \begin{equation}
    u^\mu (\xmu, \refmu) \geq u^\mu(i', \refmu) \hspace{1cm} \forall i' \in S^\mu.
  \end{equation}

@@

    Average regret, for agent $\mu$ is defined as

    \begin{equation}
      R^{\mu} = \max_{i' \in S^\mu} \Big\{ \frac{1}{T} \int_{0}^{T} u^{\mu}(\pure{\mu}{i'}, \sigma(t)) - u^{\mu}(m^\mu(t), \sigma(t)) \, dt \Big\},
    \end{equation}

    in which $\pure{\mu}{i}$ denotes the probability vector in $\Delta_\mu$ with $1$ in the slot
    $i'$ and $0$ everywhere else. Note, this is the \emph{average regret} for the agent $\mu$
    and, of course, can be related to the \emph{cumulative regret} which is used for analysis
    in \cite{Leonardos2020, Cesa-Bianchi2021}.  To illustrate the average regret, let us
    consider the case where each agent has only two actions. Then $u^{\mu}(x^\mu(t), \sigma(t))$
    is given by

    \begin{equation}
      u^{\mu}(x^\mu(t), \sigma(t)) = \sum_{ij} a_{ij} x_i^\mu \sigma_j^\mu = a_{11} x_1^\mu \sigma_1^\mu + a_{12} x_1^\mu \sigma_2^\mu + a_{21} x_2^\mu \sigma_1^\mu + a_{22} x_2^\mu \sigma_2^\mu
    \end{equation}

@@

@@

  \subsection{Non-convergent examples} \label{sec::NonConv}
  The purpose of this section is to show that, whilst wwe have shown that it converges in zero-sum games, NA-CTFP is not guaranteed to converge in general games, and can in fact give rise to a rich variety of dynamics.

  As a example of nonconvergence we consider the Shapley family of games \cite{Shapley2016}. In a two player bimatrix game $(A_\beta, B_\beta)$ this is given by

  \begin{equation}
    A_\beta = \begin{bmatrix}
      1 & 0 & \beta \\
      \beta & 1 & 0 \\
      0 & \beta & 1
    \end{bmatrix}, \; B_\beta =  \begin{bmatrix}
      - \beta & 1 & 0 \\
      0 & -\beta & 1 \\
      1 & 0 & -\beta
    \end{bmatrix}
  \end{equation}

  where $\beta \in (0, 1)$. In \cite{VanStrien2011} this was shown to produce both periodic and chaotic behaviour for different choices of $\beta$.

@@

  As an adaptation, we take the example of a three player chain, as depicted in Figure \ref{fig::ThreePlayerNetwork}. In this example, we first assume that the network is simple (i.e. there are no self-loops and $w^{\mu \mu} = 0$). The aggregation matrix can be given as

  \begin{equation}
    W = \begin{bmatrix}
      0 & 1 & 0 \\
      w & 0 & 1 - w \\
      0 & 1 & 0
    \end{bmatrix}, \; w \in (0, 1).
  \end{equation}

  We first consider the zero-sum case to show that it does indeed converge to an equilibrium as expected. Note that the zero-sum condition given for the three player chain is given as

  \begin{equation}
    x \cdot A y + y \cdot B (w x + (1-w)z) + z \cdot C y = 0. \hspace{0.5cm} \forall x, y, z \in \Delta_1 \times \Delta_2 \times \Delta_3
  \end{equation}

  in which we use the notation that $x, y, z$ (resp. $A, B, C$) denote the strategies (resp. payoffs) of agents 1, 2 and 3 respectively. This condition is satisfied if we fix $B$ and choose

  \begin{align} \label{eq::zeroSumShapley}
    A & = - w B^T \nonumber \\
    C & = - (1 - w) B^T. 
  \end{align}

@@

  Let us now make the slight modification in the definition of C so that

  \begin{equation} \label{eq::nonzeroSumShapley}
    C  = - (1 - w) B, 
  \end{equation}

  with no alteration to $A$. The modification itself is small, however it results in the zero-sum
  assumption being violated. With the same choices of $\beta$ and $w$, this results in the periodic
  orbit seen in Figures \ref{fig::nonconvergentShapley}. Here,
  the orbits reach a stable limit cycle which to be centred around the interior NE.

@@

  The fictitious play process in NA games requires that, at each time step, an agent takes a
  `measurement' of the aggregate strategy of its neighbours. It is on this measurement that they
  update their own strategy. It stands to reason then, that in real environments this measurement
  may be corrupted by noise.

  As such, we investigate the effect that introducing additive noise has
  on NA-CTFP in a zero-sum NA game. We do this in the following manner: at each time step, the
  reference signal $\refmu(t)$ is adjusted to $\refmu + \gamma \xi$ where $\xi$ is drawn from the
  standard normal distribution (zero mean and unit variance). By varying $\gamma$, we vary the
  strength of the noise. We vary $\gamma$ up to $0.5$ since, above this value, noisy measurements
  are likely to lie outside of the simplex. Since $\refmu$ is constrained to lie within $\Delta$, we
  can consider the range $\gamma \in [0, 0.5]$ to be the \emph{physical region}, in which noise is meaningful.

@@

\section{Concluding remarks}
	In this work, we have considered the action of the Fictitious Play learning algorithm in Network Aggregative Games and investigated its long term behaviour through a continuous time analysis. We find that, under a zero-sum condition, the algorithm converges to a fixed point. However, we find experimentally that this is not always the case. In fact, we find a family of NA games, based on the Shapley family, for which FP cycles about the NE. For these cases, we also perform a regret analysis which shows that, regardless of the type of game, the FP algorithm achieves no regret.

	We also investigate the influence of noise on the algorithm and find that even with the introduction of additive noise, FP converges to a fixed point, though not necessarily the NE. In fact, for our cyclic family of games, we find that the introduction of noise can actually remove the periodicity, resulting in FP converging to a fixed point.

	Our work opens a number of lines for future work. Most notable is the effect of noise. It would be prudent to analyse this theoretically, as was done in \cite{Perrin2020}, and consider the conditions under which FP will still converge to a fixed point. Furthermore, it would be interesting to investigate the phenomenon we report experimentally in a theoretical framework. Namely, the question of why noise breaks periodicity in FP and results in convergence to an NE should be investigated and, indeed, this is a line which we are currently pursuing.

	In addition, we note that the \emph{Mann Iteration}, a method of approximating fixed points which is investigated in \cite{Parise2020}, shares a remarkably similar structure to the discrete variant of FP. This may present an avenue by which NA-CTFP may be analysed in the case of convex cost functions.

	Finally, we note that in recent years FP in two player games has shown a remarkable variety of dynamical behaviours, including periodicity and chaos. In our work we have shown convergence to a fixed point and, through experiments, periodicity. It stands to reason, therefore, that a greater variety of dynamical behaviours exist for NA-CTFP for certain classes of games. It would be important to determine what these classes are. Short from being merely a curiosity, this would allow for the identification of games in which NA-CTFP leads to inherently unpredictable behaviour, an important question from the point of view of building Safe and Trusted AI.

@@

\bibliographystyle{acm}
\bibliography{references}

>>>>

  In this section we present our main results. First, we establish the
  existence of a Nash equilibrium in NA games, as in
  Def.~\refname{def::NE}. Then we show that the Fictitious Play
  dynamic on the NA game admits solutions (i.e., the NA-CTFP
  exists \fb{?}). Finally, we show that NA-CTFP reaches a fixed point when
  the NA game is zero-sum and that, when the network has no self-loops
  (i.e., is simple), NA-CTFP reaches a Nash Equilibrium. For the sake
  of brevity, we defer the proofs of our statements, as well as the
  standard topological arguments used to derive them to the
  supplementary material (Sections (S4 - S6)).

  As a reminder, the NE condition (Def. \ref{def::NE}) states that \fb{$\NE{\mu}$ is an NE iff}
%
  \begin{align*}
    \NE{\mu} &\in \arg\max_{x \in \Delta_\mu} u^\mu(x, w^{\mu \mu}x + \sum_{\nu \in N^\mu} w^{\mu \nu} \NE{\nu}) \nonumber  = \arg\max_{x \in \Delta_i} \bar{u}^\mu(x, \sum_{\nu \in N^\mu} w^{\mu \nu} \NE{\nu})
  \end{align*}
%
  where we can find \fb{what is?} $\bar{u}_i$ through the following argument
%  
  \begin{align}
    u^\mu(x, w^{\mu \mu} x + \sum_{\nu \in N^\nu} w_{\mu \nu} \NE{\nu}) & = x \cdot A^\mu (w^{\mu \mu} x + \sum_{\nu \in N^\mu} w_{\mu \nu} \NE{\nu}) \\
     & = x \cdot (w^{\mu \mu} A^\mu)  x + \sum_{\nu \in N^\mu} u^{\mu \nu}(x, \NE{\nu}) \\
     & =: \bar{u}^\mu(x, \sum_{\nu \in N^\mu} w^{\mu \nu} \NE{\nu}), \nonumber
  \end{align}
%  
  where $u^{\mu \nu}(\xmu, x^\nu) = \xmu \cdot A^\mu x^\nu$.

  Note
  that, in order to get this formulation, we had to use the assumption
  of payoffs being bilinear \fb{can we point to the exact step?} so that we could separate out the term in
  the weighted sum involving $x$ from $\bar{x}^\nu$.

@@

  \begin{theorem}[Existence of NE]
    Under assumption (II), namely that the payoff function achieves a bilinear property, a
    Nash equilibrium $\{\bar{x}^\mu\}_{\mu \in \agentset}$ exists.
  \end{theorem}

  \fb{can we say something about the relation between these two results? Is it the second one a corollary of the first one?}

@@

With the existence of the NA-CTFP in place \fb{?}, we can show that it converges
to a fixed point. In particular, let $\Omega(\alpha)$ be the set of
all limit points for $\alpha(t)$. Then, a NA-CTFP path is said to have
converged if $\Omega(\alpha)$ is contained within the set of Nash
Equilibria of the game. If this is for any such NA-CTFP path, then the
game is said to have the \emph{CTFP property} \fb{we do not really need to introduce this definition}. We adapt the techniques
of \ref{Ewerhart} to prove that zero-sum NA games have the CTFP
property.
%
  \begin{theorem}
    Any zero-sum NA game has the property that, for any NA-CTFP path $m$, the corresponding \fb{what?} $\alpha(t; m)$ converges to a set of fixed points.
  \end{theorem}

  We now point out that, if we choose $w^{\mu \mu}$ to be zero for all $\mu$, then the final inequality yields that, for all $\mu$
%
  \begin{equation}
    u^\mu(y, \sum_{\nu \in N^\mu} \wmunu \xnu_\infty) \leq u^\mu(\xmu_\infty, \sum_{\nu \in N^\mu} \wmunu \xnu_\infty)
  \end{equation}

  which is precisely the Nash equilibrium condition \fb{number?} in the NA game. This leads to the next result
%
  \begin{corollary}
    With the additional assumption that, for all agents $\mu$, all zero-sum NA games have the CTFP property. \fb{this statement is not well-formed.}
  \end{corollary}

@@

  In this section we aim to find some convergence structure \fb{?} for the
  case in which the NA game is not necessarily zero-sum. In
  particular, we show that the NA-CTFP process converges to the set of
  coarse correlated equilibria \cite{Nisan2007}.
  %
  \begin{definition}[CCE]
    A distribution $\mathcal{D}$ over the joint action set $S =
    \times_\mu S^\mu$ is called a \emph{coarse correlated equilibrium}
     if, for all $\mu$
    \begin{equation}
      \mathbb{E}_{s \sim \mathcal{D}}[u^\mu (s^\mu, s^{- \mu})] \geq
      \mathbb{E}_{x \sim \mathcal{D}}[u^\mu (j, s^{-
          \mu})] \hspace{1cm} \forall j \in S^\mu.
    \end{equation}
  \end{definition}

@@

  For an NA game, if a set of actions $s = (s^1, \ldots, s^N)$ \fb{$s$ is normally used for actions} is
  drawn from a joint probability distribution $\mathcal{D}$, then
  there is a corresponding set of reference vectors $\sigma =
  (\sigma^1, \ldots, \sigma^N)$, where $\sigma^\mu = \sum_{\nu \in
    N^\mu} \wmunu s^\nu$.  Therefore, $\mathcal{D}$ is a probability
  distribution over all actions and all references.  Consider, then, a
  vector of joint distributions over actions and references which is
  generated by NA-CTFP. In particular, if by playing with NA-CTFP, the
  agents reach the state $(\xmu)_{i = 1}^N$ with references
  $(\refmu)_{i = 1}^N$, this is the vector $\mathcal{D} =
  (\mathcal{D}^1, ..., \mathcal{D}^N)$ such that
  $(\mathcal{D}^\mu)_{ij} = \xmu_i \refmu_j$. Then, the expected
  payoff that the agent would receive for playing this strategy is
%
  \begin{align*}
    u^\mu(\xmu, \refmu) & = \xmu \cdot A^\mu \refmu = \sum_{i, j} (A^\mu)_{ij} \xmu_i \refmu_j \nonumber 
  \end{align*}

  As such, we would say that NA-CTFP has converged to the set of CCE if, in the limit of $t
  \rightarrow \infty$, we have that for all agents $\mu$,
%  \begin{equation}
  $u^\mu (\xmu, \refmu) \geq u^\mu(i', \refmu)$
  %\hspace{1cm} \
  for all $i' \in S^\mu$.
%  \end{equation}

@@

    Average regret, for agent $\mu$ is defined as
%
    \begin{equation}
      R^{\mu} = \max_{i' \in S^\mu} \Big\{ \frac{1}{T} \int_{0}^{T} u^{\mu}(\pure{\mu}{i'}, \sigma(t)) - u^{\mu}(m^\mu(t), \sigma(t)) \, dt \Big\},
    \end{equation}

    in which $\pure{\mu}{i}$ denotes the probability vector in $\Delta_\mu$ with $1$ in the slot
    $i'$ and $0$ everywhere else. Note, this is the \emph{average regret} for the agent $\mu$
    and, of course, can be related to the \emph{cumulative regret} which is used for analysis
    in \cite{Leonardos2020, Cesa-Bianchi2021}.  To illustrate the average regret, let us
    consider the case where each agent has only two actions. Then $u^{\mu}(x^\mu(t), \sigma(t))$
    is given by
%    
    \begin{equation}
      u^{\mu}(x^\mu(t), \sigma(t)) = \sum_{ij} a_{ij} x_i^\mu \sigma_j^\mu = a_{11} x_1^\mu \sigma_1^\mu + a_{12} x_1^\mu \sigma_2^\mu + a_{21} x_2^\mu \sigma_1^\mu + a_{22} x_2^\mu \sigma_2^\mu
    \end{equation}

@@

    \fb{It is not clear to me the relation between CCE and no regret. In particular, why is the following the case?}

@@

  \subsection{Non-convergent examples} \label{sec::NonConv}

  The purpose of this section is to show that, whilst we proved in \fb{?}
  %have shown
  that it converges in zero-sum games, NA-CTFP is not guaranteed to
  converge in general games, and can in fact give rise to a rich
  variety of dynamics.

  As a example of nonconvergence we consider the Shapley family of games \cite{Shapley2016}. In a two player bimatrix game $(A_\beta, B_\beta)$ this is given by
%
  \begin{equation}
    A_\beta = \begin{bmatrix}
      1 & 0 & \beta \\
      \beta & 1 & 0 \\
      0 & \beta & 1
    \end{bmatrix}, \; B_\beta =  \begin{bmatrix}
      - \beta & 1 & 0 \\
      0 & -\beta & 1 \\
      1 & 0 & -\beta
    \end{bmatrix}
  \end{equation}

  where $\beta \in (0, 1)$. In \cite{VanStrien2011} this was shown to produce both periodic and chaotic behaviour for different choices of $\beta$. \fb{do we need to provide this example?}

@@

  As an adaptation, we take the example of a three player chain, as
  depicted in Figure \ref{fig::ThreePlayerNetwork} \fb{do we need this
    figure? it is rather simple}. In this example, we first assume
  that the network is simple (i.e. there are no self-loops and $w^{\mu
    \mu} = 0$). The aggregation matrix can be given as
%
  \begin{equation}
    W = \begin{bmatrix}
      0 & 1 & 0 \\
      w & 0 & 1 - w \\
      0 & 1 & 0
    \end{bmatrix}, \; w \in (0, 1).
  \end{equation}

  We first consider the zero-sum case to show that it does indeed converge to an equilibrium as expected. Note that the zero-sum condition given for the three player chain is given as
%
  \begin{equation}
    x \cdot A y + y \cdot B (w x + (1-w)z) + z \cdot C y = 0. \hspace{0.5cm} \forall x, y, z \in \Delta_1 \times \Delta_2 \times \Delta_3
  \end{equation}
  %
  in which we use the notation that $x, y, z$ (resp. $A, B, C$) denote the strategies (resp. payoffs) of agents 1, 2 and 3 respectively. This condition is satisfied if we fix $B$ and choose
%
  \begin{align} \label{eq::zeroSumShapley}
    A & = - w B^T \nonumber \\
    C & = - (1 - w) B^T. 
  \end{align}

@@

  Let us now make the slight modification in the definition of $C$ so that
%
%  \begin{equation} \label{eq::nonzeroSumShapley}
    $C  = - (1 - w) B$, 
%  \end{equation}
  with no alteration to $A$. The modification itself is small, however it results in the zero-sum
  assumption being violated. With the same choices of $\beta$ and $w$, this results in the periodic
  orbit seen in Figures \ref{fig::nonconvergentShapley}. Here,
  the orbits reach a stable limit cycle which to be centred around the interior NE.

@@

  The fictitious play process in NA games requires that, at each time step, an agent takes a
  `measurement' of the aggregate strategy of its neighbours. It is on this measurement that they
  update their own strategy. It stands to reason then, that in real environments this measurement
  may be corrupted by noise. 
%  
  As such, we investigate the effect that introducing additive noise has
  on NA-CTFP in a zero-sum NA game. We do this in the following manner: at each time step, the
  reference signal $\refmu(t)$ is adjusted to $\refmu + \gamma \xi$ where $\xi$ is drawn from the
  standard normal distribution (zero mean and unit variance). By varying $\gamma$, we vary the
  strength of the noise. We vary $\gamma$ up to $0.5$ since, above this value, noisy measurements
  are likely to lie outside of the simplex. Since $\refmu$ is constrained to lie within $\Delta$, we
  can consider the range $\gamma \in [0, 0.5]$ to be the \emph{physical region}, in which noise is meaningful.

@@

\section{Concluding remarks}
	In this work, we have considered the action of the Fictitious Play learning algorithm in Network Aggregative Games and investigated its long term behaviour through a continuous time analysis. We find that, under a zero-sum condition, the algorithm converges to a fixed point \fb{what kind of FP? we might want to mention individual theorems}. However, we find experimentally that this is not always the case. In fact, we find a family of NA games, based on the Shapley family, for which FP cycles about the NE. For these cases, we also perform a regret analysis which shows that, regardless of the type of game, the FP algorithm achieves no regret. 
%	
	We also investigate the influence of noise on the algorithm and find that even with the introduction of additive noise, FP converges to a fixed point, though not necessarily the NE. In fact, for our cyclic family of games, we find that the introduction of noise can actually remove the periodicity, resulting in FP converging to a fixed point.

	Our work opens a number of lines for future work. Most notable is the effect of noise. It would be prudent to analyse this theoretically, as was done in \cite{Perrin2020}, and consider the conditions under which FP will still converge to a fixed point. Furthermore, it would be interesting to investigate the phenomenon we report experimentally in a theoretical framework. Namely, the question of why noise breaks periodicity in FP and results in convergence to an NE should be investigated and, indeed, this is a line which we are currently pursuing.
%	
	In addition, we note that the \emph{Mann Iteration}, a method of approximating fixed points which is investigated in \cite{Parise2020}, shares a remarkably similar structure to the discrete variant of FP. This may present an avenue by which NA-CTFP may be analysed in the case of convex cost functions. 
%	
	Finally, we note that in recent years FP in two player games has shown a remarkable variety of dynamical behaviours, including periodicity and chaos. In our work we have shown convergence to a fixed point and, through experiments, periodicity. It stands to reason, therefore, that a greater variety of dynamical behaviours exist for NA-CTFP for certain classes of games. It would be important to determine what these classes are. Short from being merely a curiosity, this would allow for the identification of games in which NA-CTFP leads to inherently unpredictable behaviour, an important question from the point of view of building Safe and Trusted AI.

@@

\bibliographystyle{named}
\bibliography{referencesT}
